---
title: "Tikz Gallery"
author: "Alfonso R. Reyes"
output:
  html_document:
    css: style.css
    keep_md: true
    toc: true
    number_sections: false
---

Implementing a tag system based of identifiers that are included in the filename. 

* Characters that pass this script: `@`, `!`, `=`, `+`.
* Character that do not pass: `#`.

**Selecting the equal symbol `=`.**


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
               comment = NA,
               results = "asis",
               error = FALSE,
               warning = FALSE,
               message = FALSE)
a <- "```tex"
b <- "```"
```

```{r, include=FALSE}
# add file suffix for file selection
suffix <- ""
ext <- "png"
pattern <- paste0("^", suffix, ".*", "\\.", ext, "$")


file.remove("child.Rmd")
tmp <- readLines("template.Rmd")

# get all PGF files
pgf <- sub(x = list.files(path = "./src/", pattern = "*.pgf"),
           pattern = "\\.pgf$",
           replacement = "")

tex <- sub(x = list.files(path = "./src/", pattern = "*.tex"),
           pattern = "\\.tex$",
           replacement = "")

# get all PNG files
png <- sub(x = list.files(path = "./src/", pattern = pattern),
           pattern = "\\.png$",
           replacement = "")

print(length(png))

# Lista de arquivos que tem os pares pgf e png.
# i <- intersect(pgf, png)
i <- intersect(tex, png)

```

```{r include=FALSE}
# create notebook child.Rmd
sapply(i,
       FUN = function(i){
           tmpi <- gsub(x = tmp,
                        pattern = "&PGF_FILE&",
                        replacement = i)
           cat(tmpi,
               file = "child.Rmd",
               append = TRUE,
               sep= "\n")
       })
```


This is my collection, or gallery, of Tikz Art.  

There are `r length(i)` Tikz figures in this gallery. 

These are coming from ...


This repository is maintained in to Git Version Control and is hosted on `___` .


The figures are sorted by filename.


Some useful tutorials or galleries:

  * <https://tobiw.de/en/teotm/tikz-adventskalender>.
  * <http://math.et.info.free.fr/TikZ/bdd/TikZ-Impatient.pdf>.
  * <http://www.mat.ufpb.br/lenimar/introtikz.pdf>.
  

Source: https://github.com/walmes/Tikz
Web: http://leg.ufpr.br/~walmes/Tikz/  

```{r, child = "child.Rmd"}
```
